Dependently Typed Multi-stage Calculus

### 2019-11-26 slides/main.tex
Finished making third draft.

\begin{frame}[fragile]{Our Approach: \LMD}
    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
    \begin{itemize}
        \item Features of multi-stage programming
        \item Features of dependent types
    \end{itemize}
    Our contribution
    \begin{itemize}
        \item Define typing, kinding, well-formed kind rules for multi-stage calculus
        \item Define equivalence rules including CSP
    \end{itemize}
    \note{
        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
        We call our multi-stage calculus as \LMD.
    }
\end{frame}

@@

    Want to use \( \text{mul5} \) in a code value.
    \begin{exampleblock}{}
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{stage }0}\ x = 5 * x\ \textbf{in} \TB\ \underbrace{(\% \text{mul5}\ 4)}_{\text{stage }1} \)
    \end{center}
    \end{exampleblock}
    CSP symbol \( \% \) {\bf{lift up}} mul5 from stage 0 to stage 1.
\end{frame}

@@

\begin{frame}[fragile]{Conclusion}
    We introduced dependent types into multi-stage calculus.
    \begin{itemize}
        \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
        \item Define equality rules.
            \begin{itemize}
                \item Especially, dealing with CSP.
            \end{itemize}
        \item Prove type soundness.
        \item Future work: algorithmic typing
    \end{itemize}
    \note{
    }
\end{frame}

>>>>

\begin{frame}[fragile]{Our Approach: \LMD}
    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
    \begin{itemize}
        \item Features of multi-stage programming
        \item Features of dependent types
    \end{itemize}
    Our contribution
    \begin{itemize}
        \item Prevent illegal use of generated code values with dependent types.
    \end{itemize}
    \note{
        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
        We call our multi-stage calculus as \LMD.
    }
\end{frame}

@@

    \begin{exampleblock}{}
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{stage }0}\ x = 5 * x\ \textbf{in} \TB\ \underbrace{(\% \text{mul5}\ 4)}_{\text{stage }1} \)
    \end{center}
    \end{exampleblock}
    CSP symbol \( \% \) {\bf{lift up}} mul5 from stage 0 to stage 1.
\end{frame}

@@

\begin{frame}[fragile]{Conclusion}
    We introduced dependent types into multi-stage calculus.
    \begin{itemize}
        \item Avoid illegal use of generated code values with dependent types.
        \item Prove type soundness.
        \item Future work: algorithmic typing
    \end{itemize}
    \note{
    }
\end{frame}
